Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-04-19 doc/thesis/results.Rnw
Finished draft intro!

<<setup, include=FALSE>>=
    library(netabc)
    library(Hmisc)
@

@@

    pp <- function (p) {
        if (p < 1e-5) {
            "<10^{-5}"
        } else {
            latexSN(round(p, -floor(log10(p))))
        }
    }

@@

Trees simulated under different values of \gls{alpha} were visibly quite
distinct (\cref{fig:alphatrees}). In particular, higher values of \gls{alpha}
produce networks with a small number of highly connected nodes which, once
infected, are likely to transmit to many other nodes. This results in a more
unbalanced, ladder-like structure in the phylogeny, compared to networks with
lower \gls{alpha} values. None of the other three parameters produced trees
which were as easily distinguished from each other
(\cref{fig:Itrees,fig:mtrees,fig:Ntrees,fig:Itrees}).
Sackin's index, which measures tree imbalance, was significantly correlated with
all four parameters
    (for $\alpha$, $I$, $m$, and $N$ respectively: Spearman's rho =
     \Sexpr{round(alpha.sackin.cor$estimate, 2)},
     \Sexpr{round(I.sackin.cor$estimate, 2)},
     \Sexpr{round(m.sackin.cor$estimate, 2)},
     \Sexpr{round(N.sackin.cor$estimate, 2)};
     $p$-values
     $\Sexpr{pp(alpha.sackin.cor$p.value)}$,
     $\Sexpr{pp(I.sackin.cor$p.value)}$,
     $\Sexpr{pp(m.sackin.cor$p.value)}$,
     $\Sexpr{pp(N.sackin.cor$p.value)}$)
The ratio of internal to terminal branch lengths was negatively correlated with
\gls{alpha} and \gls{I}, and positively corelated with \gls{N} and \gls{m}
  (Spearman's rho
    \Sexpr{round(alpha.ratio.cor$estimate, 2)},
    \Sexpr{round(I.ratio.cor$estimate, 2)},
    \Sexpr{round(m.ratio.cor$estimate, 2)},
    \Sexpr{round(N.ratio.cor$estimate, 2)};
  $p$-values
    $\Sexpr{latexSN(round(alpha.ratio.cor$p.value, -floor(log10(alpha.ratio.cor$p.value))))}$,
    $\Sexpr{latexSN(round(I.ratio.cor$p.value, -floor(log10(I.ratio.cor$p.value))))}$,
    $\Sexpr{latexSN(round(m.ratio.cor$p.value, -floor(log10(m.ratio.cor$p.value))))}$,
    $\Sexpr{latexSN(round(N.ratio.cor$p.value, -floor(log10(N.ratio.cor$p.value))))}$).

@@

\Cref{fig:kpca} shows \gls{kPCA} projections of the simulated trees onto the
first two principal components of the kernel matrix. The figure shows only the
simulations with 500-tip trees and, for all parameters except $I$, 1000
infected nodes. The three \gls{alpha} and \gls{I} values considered are well
separated from each other in feature space. On the other hand, the three
\gls{N} values overlap significantly, and the three \gls{m} values are
virtually indistinguishable. Similar observations can be made for other values
of \gls{I} and the number of tips
(\cref{fig:alphakpca,fig:Nkpca,fig:Ikpca,fig:mkpca}). The values of \gls{I} and
\gls{N} separate more clearly with larger numbers of tips, and in the case of
\gls{N} larger epidemic sizes.

@@

Accuracy of the \gls{kSVM} classifiers varied based on the parameter being
tested (\cref{fig:rsquared}, left). Classifiers based on two other tree
statistics, the \gls{nltt} and Sackin's index, generally exhibited worse
performance than the tree kernel, although the magnitude of the disparity
varied between the parameters (\cref{fig:rsquared}, centre and right). The
results were largely robust to variations in the tree kernel meta-parameters
$\lambda$ and $\sigma$, although accuracy varied between different epidemic and
sampling scenarios
(\cref{fig:alphacrossv,fig:mcrossv,fig:Icrossv,fig:Ncrossv}).

When classifying $\alpha$, the kernel-SVM classifier had an average $R^2$ of 
    \Sexpr{kernel.alpha[,round(mean(rsquared), 2)]},
compared to 
    \Sexpr{nltt.alpha[,round(mean(rsquared), 2)]}
for the \gls{nltt}-based SVM, and
    \Sexpr{sackin.alpha[,round(mean(rsquared), 2)]}
for the linear regression against Sackin's index. There was little variation
about the mean for different tree and epidemic sizes. No classifier could
accurately identify the $m$ parameter in any epidemic scenario, with average
$R^2$ values of 
  \Sexpr{kernel.m[,round(mean(rsquared), 2)]} for \gls{kSVM},
  \Sexpr{nltt.m[,round(mean(rsquared), 2)]} for the \gls{nltt}, and
  \Sexpr{sackin.m[,round(mean(rsquared), 2)]}
for Sackin's index. Again, there was little variation in accuracy between
epidemic scenarios, although the accuracy of the \gls{kSVM} was slightly higher
on 1000-tip trees.

The accuracy of classifiers $I$ varied significantly with the number of tips in
the tree. For 100-tip trees, the average $R^2$ values were
  \Sexpr{kernel.I[ntip == 100, round(mean(rsquared), 2)]},
  \Sexpr{nltt.I[ntip == 100, round(mean(rsquared), 2)]}, and
  \Sexpr{sackin.I[ntip == 100, round(mean(rsquared), 2)]}
for the tree kernel, \gls{nltt}, and Sackin's index respectively. For 500-tip
trees, the values increased to
  \Sexpr{kernel.I[ntip == 500, round(mean(rsquared), 2)]},
  \Sexpr{nltt.I[ntip == 500, round(mean(rsquared), 2)]}, and
  \Sexpr{sackin.I[ntip == 500, round(mean(rsquared), 2)]}.
Finally, the performance of classifiers for $N$ depended heavily on the
epidemic scenario. The $R^2$ of the \gls{kSVM} classifier ranged from
  \Sexpr{kernel.N[,round(min(rsquared), 2)]}
for the smallest epidemic and smallest sample size, to
  \Sexpr{kernel.N[,round(max(rsquared), 2)]}
for the largest. Likewise, $R^2$ for the \gls{nltt}-based SVM ranged from 
  \Sexpr{nltt.N[,round(min(rsquared), 2)]}
to
  \Sexpr{nltt.N[,round(max(rsquared), 2)]}.
Sackin's index did not accurately classify $N$ in any scenario, with an average
$R^2$ of
  \Sexpr{sackin.N[,round(mean(rsquared), 2)]}
and little variation between scenarios.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{kernel-rsquared.pdf}
  \caption{
      Cross-validation accuracy of kernel-SVM classifier (left), SVM classifier
      using \gls{nltt} (centre), and linear regression using Sackin's index
      (right) for \gls{BA} model parameters. Kernel meta-parameters were set to
      $\lambda = 0.3$ and $\sigma = 4$. Each point was calculated based on 300
      simulated transmission trees over networks with three different values of
      the parameter being tested. Vertical lines are empirical 95\% confidence
      intervals based on 1000 two-fold cross-validations.
  }
  \label{fig:rsquared}
\end{figure}

@@

The accuracy of grid search estimates largely paralleled that of the \gls{kSVM}
classifiers. \Cref{fig:gridest} shows point estimates and 95\% highest density
intervals for each of the \gls{BA} parameters, for one replicate experiment
with 500-tip trees. For all parameters except $m$, the error of point estimates
was negatively correlated with the number of sampled tips in the tree (for
\gls{alpha}, \gls{I}, and \gls{N} respectively: Spearman's $\rho$ = 
    \Sexpr{tip.cor["alpha", round(estimate, 2)]},
    \Sexpr{tip.cor["I", round(estimate, 2)]},
    \Sexpr{tip.cor["N", round(estimate, 2)]};
$p$-value = 
    $\Sexpr{tip.cor["alpha", latexSN(round(p.value, -floor(log10(p.value))))]}$,
    $\Sexpr{tip.cor["I", latexSN(round(p.value, -floor(log10(p.value))))]}$,
    $\Sexpr{tip.cor["N", latexSN(round(p.value, -floor(log10(p.value))))]})$.
The highest density intervals obtained for all parameters were extremely wide,
occcupying $>$90\% of the grid in all cases.

The \gls{alpha} parameter was the most accurately estimated, with point
estimates having an average deviation of 
    \Sexpr{d[parameter == "alpha", round(mean(error), 2)]}
from the true value, on a grid from 0 to 2. The error was negatively correlated
with the true value of \gls{alpha} 
    (Spearman's $\rho$ = \Sexpr{value.cor["alpha", round(estimate, 2)]},
     $p = \Sexpr{value.cor["alpha", latexSN(round(p.value, -floor(log10(p.value))))]}$),
although the relationship was clearly nonlinear (\cref{fig:gridest,fig:gridalpha}).
The accuracy was highest for the test value \gls{alpha} = 1.25
    (mean error \Sexpr{d[parameter == "alpha" & true_value == 1.25, round(mean(error), 2)]})
which exhibited markedly different behaviour than the other values in terms of
the distribution of kernel scores along the grid (\cref{fig:gridalpha}). In
particular, there was a very pronounced peak in scores around the true value,
in contrast to most other values where the scores were flat around the true
value. The peak was also observed to a lesser degree for \gls{alpha} = 1. The
average absolute error of the point estimates for \gls{I} was 
    \Sexpr{d[parameter == "I", round(mean(error))]},
on a grid of 500 to 5000, and the errors were not significantly correlated with
the true value of \gls{I}. Kernel score distributions for all test values
exhibited the same rounded shape (\cref{fig:gridI}).

For the other two parameters, \gls{m} and \gls{N}, accuracy was much poorer
(\cref{fig:gridest,fig:gridm,fig:gridN}). The average error for \gls{m} was
    \Sexpr{d[parameter == "m", round(mean(error), 2)]},
on a grid from 1 to 6; this error was positively correlated with increasing
\gls{m}
    (Spearman's $\rho$ = \Sexpr{value.cor["m", round(estimate, 2)]},
     $p = \Sexpr{value.cor["m", latexSN(round(p.value, -floor(log10(p.value))))]}$).
This positive correlation was apparently due to the much lower error for $m =
1$ than for the other $m$ values (\cref{fig:gridm})
    (mean errors \Sexpr{d[parameter == "m" & true_value == 1, mean(error)]} for
     $m = 1$ vs. \Sexpr{d[parameter == "m" & true_value > 1, mean(error)]} for
     $m > 1$).
The value $m = 1$ causes the network to take on a distinct shape relative to
higher $m$ values, namely a tree (\textit{i.e.} there are no cycles,
\cref{subsec:treeshape}). The average error for \gls{N} was 
    \Sexpr{d[parameter == "N", round(mean(error))]},
on a grid from 1000 to 15000, and was positively correlated with the true value
of \gls{N}
    (Spearman's $\rho$ = \Sexpr{value.cor["N", round(estimate, 2)]},
     $p = \Sexpr{value.cor["N", latexSN(round(p.value, -floor(log10(p.value))))]}$).

@@

    alpha.av <- anova(lm(alpha_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    m.av <- anova(lm(m_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    N.av <- anova(lm(N_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    I.av <- anova(lm(I_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))

    m.tbl <- d[,prop.table(table(m_error))]
    zero.alpha.test <- wilcox.test(d[true_alpha == 0, alpha_error], 
                                   d[true_alpha != 0, alpha_error])
    alpha.I.test <- wilcox.test(d[true_alpha < 1, I_error],
                                d[true_alpha >= 1, I_error])
    I.I.test <- wilcox.test(d[true_I == 1000, I_error],
                            d[true_I == 2000, I_error])
    alpha.m.test <- wilcox.test(d[true_alpha == 0 | true_alpha == 1, m_error],
                                d[true_alpha == 0.5 | true_alpha == 1.5, m_error])

    options(scipen=-1, digits=2)
@

We used kernel-\gls{ABC} to estimate the parameters of the \gls{BA} model 
on simulated trees where the true parameter values were known. Point estimates
for each parameter are shown in Figure~\ref{fig:abcpt}. Of the four parameters,
\gls{alpha} was the most accurately estimated, with a median [IQR] absolute error
of 
    \Sexpr{d[,median(alpha_error)]} 
    [\Sexpr{d[,quantile(alpha_error, 0.25)]}-\Sexpr{d[,quantile(alpha_error, 0.75)]}].
The accuracy of the estimates was not significantly different between values of
$m$ or $I$ (both one-way ANOVA,
    $p$ = \Sexpr{alpha.av["factor(true_m)", "Pr(>F)"]}
and 
    \Sexpr{alpha.av["factor(true_I)", "Pr(>F)"]}),
although the errors when the true value of \gls{alpha} was zero were
significantly greater than the other values 
    (Wilcoxon rank-sum test, $p$ = \Sexpr{zero.alpha.test$p.value}).
The error in the estimated value of $I$ was
    \Sexpr{d[,round(median(I_error))]} 
    [\Sexpr{d[,round(quantile(I_error, 0.25))]}-\Sexpr{d[,round(quantile(I_error, 0.75))]}].
Errors were significantly higher for $\alpha \geq 1$
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.I.test$p.value})
and for $I$ = 2000
    ($p$ = \Sexpr{I.I.test$p.value}),
but not for any values of $m$
    (one-way ANOVA, $p$ = \Sexpr{I.av["factor(true_m)", "Pr(>F)"]}).
The $m$ parameter was estimated correctly in
    \Sexpr{as.integer(m.tbl[1] * 100)} \%
of simulations, with an error of one in
    \Sexpr{as.integer(m.tbl[2] * 100)} \%
and of two or more in 
    \Sexpr{as.integer(sum(m.tbl[3:length(m.tbl)]) * 100)} \%
(the only possible $m$ values were 2, 3, 4, or 5). The true values of
$m$ and $I$ did not significantly affect the error
    (one-way ANOVA, $p$ = \Sexpr{m.av["factor(true_m)", "Pr(>F)"]} and
                          \Sexpr{m.av["factor(true_I)", "Pr(>F)"]}),
but the accuracy was significantly lower for integral than non-integral
values of \gls{alpha}
    (Wilcoxon rank-sum test, $p$ = \Sexpr{alpha.m.test$p.value}).
Finally, the total number of nodes \gls{N} was consistently over-estimated by
about a factor of two
    (error \Sexpr{d[,median(N_error)]} 
    [\Sexpr{d[,quantile(N_error, 0.25)]}-\Sexpr{d[,quantile(N_error, 0.75)]}]).
No other parameters influenced the accuracy of the $N$ estimates 
    (one-way ANOVA, $p \geq$ \Sexpr{min(N.av[,"Pr(>F)"])}).

>>>>

<<setup, include=FALSE>>=
    library(netabc)
    library(Hmisc)

    pp <- function (p) {
        if (p < 1e-5) {
            "{<}10^{-5}"
        } else {
            latexSN(round(p, -floor(log10(p))))
        }
    }
@

@@

@@

Trees simulated under different values of \gls{alpha} were visibly quite
distinct (\cref{fig:alphatrees}). In particular, higher values of \gls{alpha}
produce networks with a small number of highly connected nodes which, once
infected, are likely to transmit to many other nodes. This results in a more
unbalanced, ladder-like structure in the phylogeny, compared to networks with
lower \gls{alpha} values. None of the other three parameters produced trees
which were as easily distinguished from each other
(\cref{fig:Itrees,fig:mtrees,fig:Ntrees,fig:Itrees}).
Sackin's index, which measures tree imbalance, was significantly correlated with
all four parameters
    (for $\alpha$, $I$, $m$, and $N$ respectively: Spearman's rho =
     \Sexpr{round(alpha.sackin.cor$estimate, 2)},
     \Sexpr{round(I.sackin.cor$estimate, 2)},
     \Sexpr{round(m.sackin.cor$estimate, 2)},
     \Sexpr{round(N.sackin.cor$estimate, 2)};
     $p$-values
     $\Sexpr{pp(alpha.sackin.cor$p.value)}$,
     $\Sexpr{pp(I.sackin.cor$p.value)}$,
     $\Sexpr{pp(m.sackin.cor$p.value)}$,
     $\Sexpr{pp(N.sackin.cor$p.value)}$)
The ratio of internal to terminal branch lengths was negatively correlated with
\gls{alpha} and \gls{I}, and positively corelated with \gls{N} and \gls{m}
  (Spearman's rho
    \Sexpr{round(alpha.ratio.cor$estimate, 2)},
    \Sexpr{round(I.ratio.cor$estimate, 2)},
    \Sexpr{round(m.ratio.cor$estimate, 2)},
    \Sexpr{round(N.ratio.cor$estimate, 2)};
  all $p < 10^{-5}$).

@@

\Cref{fig:kpca} shows \gls{kPCA} projections of the simulated trees onto the
first two principal components of the kernel matrix. The figure shows only the
simulations with 500-tip trees and 1000 infected nodes. The three \gls{alpha}
and \gls{I} values considered are well separated from each other in feature
space. On the other hand, the three \gls{N} values overlap significantly, and
the three \gls{m} values are virtually indistinguishable. Similar observations
can be made for other values of \gls{I} and the number of tips
(\cref{fig:alphakpca,fig:Nkpca,fig:Ikpca,fig:mkpca}). The values of \gls{I} and
\gls{N} separated more clearly with larger numbers of tips, and in the case of
\gls{N}, larger epidemic sizes.

@@

Accuracy of the \gls{kSVR} classifiers varied based on the parameter being
tested (\cref{fig:rsquared}, left). Classifiers based on two other tree
statistics, the \gls{nltt} and Sackin's index, generally exhibited worse
performance than the tree kernel, although the magnitude of the disparity
varied between the parameters (\cref{fig:rsquared}, centre and right). The
results were largely robust to variations in the tree kernel meta-parameters
$\lambda$ and $\sigma$, although accuracy varied between different epidemic and
sampling scenarios
(\cref{fig:alphacrossv,fig:mcrossv,fig:Icrossv,fig:Ncrossv}).

When classifying $\alpha$, the \gls{kSVR} classifier had an average $R^2$ of 
    \Sexpr{kernel.alpha[,round(mean(rsquared), 2)]},
compared to 
    \Sexpr{nltt.alpha[,round(mean(rsquared), 2)]}
for the \gls{nltt}-based SVR, and
    \Sexpr{sackin.alpha[,round(mean(rsquared), 2)]}
for the linear regression against Sackin's index. There was little variation
about the mean for different tree and epidemic sizes. No classifier could
accurately identify the $m$ parameter in any epidemic scenario, with average
$R^2$ values of 
  \Sexpr{kernel.m[,round(mean(rsquared), 2)]} for \gls{kSVR},
  \Sexpr{nltt.m[,round(mean(rsquared), 2)]} for the \gls{nltt}, and
  \Sexpr{sackin.m[,round(mean(rsquared), 2)]}
for Sackin's index. Again, there was little variation in accuracy between
epidemic scenarios, although the accuracy of the \gls{kSVR} was slightly higher
on 1000-tip trees 
    (average $R^2$ 
     \Sexpr{kernel.m[ntip == 100,round(mean(rsquared, 2))]},
     \Sexpr{kernel.m[ntip == 500,round(mean(rsquared, 2))]},
     \Sexpr{kernel.m[ntip == 1000,round(mean(rsquared, 2))]}
     for 100, 500, and 1000 tips respectively).

The accuracy of classifiers $I$ varied significantly with the number of tips in
the tree. For 100-tip trees, the average $R^2$ values were
  \Sexpr{kernel.I[ntip == 100, round(mean(rsquared), 2)]},
  \Sexpr{nltt.I[ntip == 100, round(mean(rsquared), 2)]}, and
  \Sexpr{sackin.I[ntip == 100, round(mean(rsquared), 2)]}
for the tree kernel, \gls{nltt}, and Sackin's index respectively. For 500-tip
trees, the values increased to
  \Sexpr{kernel.I[ntip == 500, round(mean(rsquared), 2)]},
  \Sexpr{nltt.I[ntip == 500, round(mean(rsquared), 2)]}, and
  \Sexpr{sackin.I[ntip == 500, round(mean(rsquared), 2)]}.
Finally, the performance of classifiers for $N$ depended heavily on the
epidemic scenario. The $R^2$ of the \gls{kSVR} classifier ranged from
  \Sexpr{kernel.N[,round(min(rsquared), 2)]}
for the smallest epidemic and smallest sample size, to
  \Sexpr{kernel.N[,round(max(rsquared), 2)]}
for the largest. Likewise, $R^2$ for the \gls{nltt}-based SVR ranged from 
  \Sexpr{nltt.N[,round(min(rsquared), 2)]}
to
  \Sexpr{nltt.N[,round(max(rsquared), 2)]}.
Sackin's index did not accurately classify $N$ in any scenario, with an average
$R^2$ of
  \Sexpr{sackin.N[,round(mean(rsquared), 2)]}
and little variation between scenarios.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{kernel-rsquared.pdf}
  \caption{
      Cross-validation accuracy of kernel-SVR classifier (left), SVR classifier
      using \gls{nltt} (centre), and linear regression using Sackin's index
      (right) for \gls{BA} model parameters. Kernel meta-parameters were set to
      $\lambda = 0.3$ and $\sigma = 4$. Each point was calculated based on 300
      simulated transmission trees over networks with three different values of
      the parameter being tested. Vertical lines are empirical 95\% confidence
      intervals based on 1000 two-fold cross-validations.
  }
  \label{fig:rsquared}
\end{figure}

@@

The accuracy of grid search estimates largely paralleled that of the \gls{kSVR}
classifiers. \Cref{fig:gridest} shows point estimates and 95\% highest density
intervals for each of the \gls{BA} parameters, for one replicate experiment
with 500-tip trees. For all parameters except $m$, the error of point estimates
was negatively correlated with the number of sampled tips in the tree (for
\gls{alpha}, \gls{I}, and \gls{N} respectively: Spearman's $\rho$ = 
    \Sexpr{tip.cor["alpha", round(estimate, 2)]},
    \Sexpr{tip.cor["I", round(estimate, 2)]},
    \Sexpr{tip.cor["N", round(estimate, 2)]};
$p$-values
    $\Sexpr{tip.cor["alpha", pp(p.value)]}$,
    $\Sexpr{tip.cor["I", pp(p.value)]}$,
    $\Sexpr{tip.cor["N", pp(p.value)]}$).
The highest density intervals obtained for all parameters were extremely wide,
occcupying $>$90\% of the grid in all cases (\cref{fig:gridest}).

The \gls{alpha} parameter was the most accurately estimated, with point
estimates having an average deviation of 
    \Sexpr{d[parameter == "alpha", round(mean(error), 2)]}
from the true value, on a grid from 0 to 2. The error was negatively correlated
with the true value of \gls{alpha} 
    (Spearman's $\rho$ = \Sexpr{value.cor["alpha", round(estimate, 2)]},
     $p = \Sexpr{value.cor["alpha", pp(p.value)]}$),
although the relationship was clearly nonlinear (\cref{fig:gridest,fig:gridalpha}).
The accuracy was highest for the test value \gls{alpha} = 1.25
    (mean error \Sexpr{d[parameter == "alpha" & true_value == 1.25, round(mean(error), 2)]})
which exhibited markedly different behaviour than the other values in terms of
the distribution of kernel scores along the grid (\cref{fig:gridalpha}). In
particular, there was a very pronounced peak in scores around the true value,
in contrast to most other values where the scores were flat around the true
value. The peak was also observed to a lesser degree for \gls{alpha} = 1. The
average absolute error of the point estimates for \gls{I} was 
    \Sexpr{d[parameter == "I", round(mean(error))]},
on a grid of 500 to 5000, and the errors were not significantly correlated with
the true value of \gls{I}. Kernel score distributions for all test values
exhibited a similar rounded shape (\cref{fig:gridI}).

The average error for \gls{m} was
    \Sexpr{d[parameter == "m", round(mean(error), 2)]},
on a grid from 1 to 6; this error was positively correlated with increasing
\gls{m}
    (Spearman's $\rho$ = \Sexpr{value.cor["m", round(estimate, 2)]},
     $p = \Sexpr{value.cor["m", pp(p.value)]}$).
This positive correlation was apparently due to the much lower error for
\gls{m} = 1 and 2 than for the other $m$ values 
    (mean errors 
    \Sexpr{d[parameter == "m" & true_value <= 2, round(mean(error), 2)]} 
    for $m \leq 2$ vs. 
    \Sexpr{d[parameter == "m" & true_value > 2, round(mean(error), 2)]} 
    for $m > 2$, \cref{fig:gridm}).
The value $m = 1$ causes the network to take on a distinct shape relative to
higher \gls{m} values, namely a tree (\textit{i.e.} there are no cycles,
see \cref{subsec:treeshape}). The average error for \gls{N} was 
    \Sexpr{d[parameter == "N", round(mean(error))]},
on a grid from 1000 to 15000, and was positively correlated with the true value
of \gls{N}
    (Spearman's $\rho$ = \Sexpr{value.cor["N", round(estimate, 2)]},
    $p \Sexpr{value.cor["N", pp(p.value)]}$).

@@

    alpha.av <- anova(lm(alpha_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    m.av <- anova(lm(m_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    N.av <- anova(lm(N_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    I.av <- anova(lm(I_error ~ factor(true_alpha) + factor(true_m) + factor(true_I), d))
    stopifnot(I.av["factor(true_m)", "Pr(>F)"] >= 0.05)
    stopifnot(m.av["factor(true_m)", "Pr(>F)"] >= 0.05)
    stopifnot(m.av["factor(true_I)", "Pr(>F)"] >= 0.05)
    stopifnot(min(na.omit(N.av[,"Pr(>F)"])) >= 0.05)

    m.tbl <- d[,prop.table(table(m_error))]
    zero.alpha.test <- wilcox.test(d[true_alpha == 0, alpha_error], 
                                   d[true_alpha != 0, alpha_error])
    alpha.I.test <- wilcox.test(d[true_alpha < 1, I_error],
                                d[true_alpha >= 1, I_error])
    I.I.test <- wilcox.test(d[true_I == 1000, I_error],
                            d[true_I == 2000, I_error])
    alpha.m.test <- wilcox.test(d[true_alpha == 0 | true_alpha == 1, m_error],
                                d[true_alpha == 0.5 | true_alpha == 1.5, m_error])
    options(scipen=-1, digits=2)
@

We used \software{netabc} to estimate the parameters of the \gls{BA} model on
simulated trees where the true parameter values were known. Point estimates for
each parameter are shown in \cref{fig:abcpt} for the simulations with \gls{m} =
2. The results for the other values of \gls{m} were similar
(\cref{fig:abcm3,fig:abcm4}). The median [IQR] absolute error of estimates of
\gls{alpha} across all simulations was
    \Sexpr{d[,median(alpha_error)]} 
    [\Sexpr{d[,quantile(alpha_error, 0.25)]}-\Sexpr{d[,quantile(alpha_error, 0.75)]}].
The accuracy of the estimates was not significantly different between values of
$m$ or $I$ (both one-way ANOVA,
    $p$ = \Sexpr{alpha.av["factor(true_m)", "Pr(>F)"]}
and 
    \Sexpr{alpha.av["factor(true_I)", "Pr(>F)"]}),
although the errors when the true value of \gls{alpha} was zero were
significantly greater than the other values 
    (Wilcoxon rank-sum test, $p = \Sexpr{pp(zero.alpha.test$p.value)}$).
The error in the estimated value of $I$ was
    \Sexpr{d[,round(median(I_error))]} 
    [\Sexpr{d[,round(quantile(I_error, 0.25))]}-\Sexpr{d[,round(quantile(I_error, 0.75))]}].
Errors were significantly higher for $\alpha \geq 1$
    (Wilcoxon rank-sum test, $p = \Sexpr{pp(alpha.I.test$p.value)}$)
and for $I$ = 2000
    ($p = \Sexpr{pp(I.I.test$p.value)}$),
but not for any values of $m$ (one-way ANOVA). The $m$ parameter was estimated
correctly in only
    \Sexpr{as.integer(m.tbl[1] * 100)} \%
of simulations. The true values of $m$ and $I$ did not significantly affect the
error (one-way ANOVA), but the accuracy was significantly lower for integral
than non-integral values of \gls{alpha}
    (Wilcoxon rank-sum test, $p = \Sexpr{pp(alpha.m.test$p.value)}$).
Finally, the total number of nodes \gls{N} was consistently over-estimated by
about a factor of two
    (error \Sexpr{d[,format(median(N_error), scientific=FALSE)]} 
    [\Sexpr{d[,format(quantile(N_error, 0.25), scientific=FALSE)]} - 
     \Sexpr{d[,format(quantile(N_error, 0.75), scientific=FALSE)]}]).
No other parameters influenced the accuracy of the $N$ estimates (one-way
ANOVA)

\begin{figure}
  \includegraphics{abc-point-estimate-m2}
  \caption{
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by         
    running \software{netabc} on simulated data. Values shown are for               
    simulations with \gls{m} = 3. Dashed lines indicate true values. (A)            
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations  
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held   
    fixed in these simulations at the values \gls{m} = 3 and \gls{N} = 5000. 
  }
  \label{fig:abcm2}
\end{figure}
